---
title: "My First Shiny Presentation"
author: "Sunaina"
date: '2022-07-05'
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instruction

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

The application must include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Slide with complete reporting application

Click below link for for Shiny Application
https://captainwoman.shinyapps.io/myShiny/

Click the link below for compiled project files on github repo
https://github.com/captainwoman/Data-Developong-Product-Project-3.git


## ui.R
```{r echo=TRUE}
library(shiny)
shinyServer(
  pageWithSidebar(
  
    headerPanel("My first Shiny App"),
  
    sidebarPanel(
      selectInput("Distribution","Please select Distribution Type",
                  choices = c("Normal","Exponential")),
      sliderInput("sampleSize","Please select Sample Size: ",
                  min = 100,max = 5000, value = 1000,step = 100),
      conditionalPanel(condition = "input.Distribution =='Normal'",
                       textInput("Mean","Please select the mean",10),
                       textInput("sd","Please select Standard Deviation",3)),
      conditionalPanel(condition = "input.Distribution== 'Exponential'",
                       textInput("lambda","Please select Exponential Lambda:",1))
    ),
    mainPanel(
      plotOutput("MyPlot")
    )
          
  )   
      
      
)
```

## server.R

```{r,echo=TRUE}
shinyServer(
function(input,output, session){
  
  output$MyPlot <- renderPlot({
    
    distTYpe <- input$Distribution
    size <- input$sampleSize
     if( distTYpe == "Normal"){
       
       randomVec <- rnorm(size, mean = as.numeric(input$Mean),sd= as.numeric(input$sd))
     }
  else{
     randomVec <- rexp(size, rate = 1/as.numeric(input$lambda))
  }
    hist(randomVec, col= "red" )
    })
}
  )
```







